We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-15 paper/paper.tex
edit

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
We build up on the suggestions made in \cite{2017AN....338..854P}.
We do not look for planes or coherent kinematical structures in the
interest of keeping the method straightforward and robust.

The method uses as a reference point the spherically randomized data
of the system under study.
We first measure the width and axis ratios for the satellite
distributions of interest. 
Then, we measure the same quantities for spherically
randomized data. 
Finally, renormalize the initial results to the mean value and
standard deviation from the randomized samples.

>>>>

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
We build up on the suggestions made in \cite{2017AN....338..854P}, 
focusing on asphericity estimates for a fixed number of the brightest
satellites around each galaxy.
In the interest of keeping the method straightforward and robust we do
not look for planes in subsets of satellites or coherent kinematical
structures.

The method uses as a reference point the spherically randomized data
of the system under study.
We first measure the width and axis ratios for the satellite
distributions of interest. 
Then, we measure the same quantities for the same set of points after
a process of spherical randomization.
Finally, we renormalize the initial results to the mean value and
standard deviation computed from the randomized data.
